---
title: "The Battle for America: Forecasting about the 2024 Presidential Election"
subtitle: "My subtitle if needed"
author: 
  - Yi Tang
  - Jin Zhang
  - Siyuan Lu
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: Nov 1, 2024
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(here)

# Load the dataset
data <- read_csv(here::here("data","analysis_data","analysis_data.csv"))

```


# Introduction

Overview paragraph


Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....






# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].There are totally 17749 observations in the original dataset. Variables in the dataset help analyze and expect the final outcome of US Presidential Election in 2024.

Below is the key variable from dataset that we used for our analysis:

Poll ID (poll_id): Uniquely identifies each poll.
Pollster (pollster): The organization that conducted the poll.
State (state): The state in which the poll was conducted.
Numeric Grade (numeric_grade): A grade assigned to the pollster based on their historical accuracy and methodology, where grades equal to or greater than 3 have been included for analysis to ensure data reliability.
Methodology (methodology): The method used for polling, such as phone, online and so on.
Start Date (start_date) and End Date (end_date): The duration over which the poll was conducted.
Sample Size (sample_size): The number of respondents in the poll.
Party (party): The political party of the candidate.
Candidate Name (candidate_name): The name of the candidate to whom the poll response pertains, originally recorded under 'answer' and renamed for clarity.
Percentage (pct): The percentage of respondents favoring the candidate.

After studying the data, we decided to select pollsters with a numeric grade greater than or equal to three because the results of such polling organizations are more meaningful. And we set candidate names to Harris and Trump, which are the two most widely watched candidates this year.

## Measurement
	
Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.



Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false
#| warning: false
#| message: false

data <- read_csv(here::here("data","analysis_data","analysis_data.csv"), show_col_types = FALSE)


```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it. 

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.








# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.


### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```




# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Methodology 
1200 sample of registered voters

#Online survey

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```



\newpage

# Appendix 1

## Population, Frame, and Sample
YouGov conducted surveys with adults in the U.S. who have internet access. They used their online group of people as the sample frame. This frame covers a wide population. For each survey, the sample includes people from this group who fit specific requirements set for that survey. This helps collect data that targets certain information.

## Sample Recruitment
YouGov worked actively to bring people into their panel. They used different ways of advertising and worked with various partners across many types of media. This method aimed to gather a wide range of people. This helps make sure the group of survey takers represents many different kinds of people in the U.S. However, it mostly includes people who can use the internet.

## Sampling Methodology
YouGov used a non-probability method to find people for their online panel through various media sources. This helps improve how well the panel represents different groups of people. This method is fast and lets them interact with the survey takers through surveys that can include videos and pictures. But, relying on people who choose to join and using digital surveys might limit who takes part and affect the survey's accuracy. They made the survey results match the general population by adjusting weights according to certain standards.

## Handling Non-Response
They managed the issue of people not responding to surveys by adjusting the survey sample's make-up. They did this using weights based on well-known data like the U.S. Census.

## Questionnaire Design
YouGov designed their questionnaires to be easy to access and interesting, often using videos and pictures to give more information. However, using digital formats might stop people with limited internet skills or access from taking part.



# References


